Numerical modelling of the Cordilleran ice sheet

### 2014-08-06 kappa.tex
Move TOC to separate page and re-arrange figures.

% ======================================================================
\onecolumn
\renewcommand{\contentsname}{Contents of cover summary}
\tableofcontents
% ======================================================================

@@

\begin{multicols}{2}  % appears necessary for adequate figure positions

@@

@@

\begin{figure}[t]
  \centering
  \includegraphics{paleo-timeseries}
  \caption{Palaeo-climate records of the last 800\,ka.
           \textbf{(a)} Benthic oxygen isotope (\chem{\delta^{18}O}) record
           from a compilation of globally-distributed deep sea sediment cores
           \citep{Lisiecki.Raymo.2005}. Higher \chem{\delta^{18}O} values
           correspond to periods of lower temperatures \citep{Emiliani.1955}
           or lower global sea level, and thus higher ice volume stored in
           glaciers and ice sheets on land \citep{Shackleton.1967}.
           \textbf{(b)} Temperature anomalies ($\Delta T$) reconstructed from a
           central Antarctic ice core \citep[EPICA Dome~C,][]{Jouzel.etal.2007}.
           The grey bands indicate the approximate time span of the last
           glacial period of 110 to 10\,ka.}
  \label{fig:paleo-timeseries}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present \citep{Patterson.Kelso.2014}, and
           \textbf{(b)} during the last glacial maximum
           \citep{Ehlers.Gibbard.2007}.}
  \label{fig:paleo-glaciation}
\end{figure}

Nevertheless, the landform record is sparse in time and, most often, spatially
incomplete. Palaeo-ice sheets did not leave a continuous imprint on the
lanscape, and much of this evidence has been overprinted by subsequent glacier
re-advances and other geomorphological processes \citep{Kleman.1994,
Kleman.etal.2006, Kleman.etal.2010}.
Therefore, geomorphological reconstructions of former glacier extent require a
substantial amount of interpretation. This is where numerical ice sheet models,
incorporating the processes of glacier sliding \citep[e.g.,][]{Weertman.1957}
and deformation \citep[e.g.,][]{Nye.1953} observed on modern glaciers, can
help. Although these models alone contain too many uncertainties to reproduce
accurate ice sheet reconstructions during former glacial cycles
\citep[e.g.,][]{Hebeler.etal.2008}, they can be calibrated against geological
data where they exist \citep{Napieralski.etal.2007}, while allowing
physics-based, quantitative reconstructions of ice sheet sectors where they do
not
\citep[e.g.,][]{Marshall.etal.2002, Tarasov.Peltier.2004}.
In addition, numerical ice sheet models provide quantitative insights on the
four-dimensional distribution of stresses and deformations in palaeo-ice sheets
and allow for reconstructions of their past thickness and volume evolution, which
are difficult to infer from geological evidence.

>>>>

\onecolumn

% ======================================================================
\hfill \textbf{\huge Cover summary}
\vfill
\tableofcontents
% ======================================================================

@@

\begin{multicols}{2}  % appears necessary for bottom figures on first page

@@

\begin{figure}
  \centering
  \includegraphics{paleo-timeseries}
  \caption{Palaeo-climate records of the last 800\,ka.
           \textbf{(a)} Benthic oxygen isotope (\chem{\delta^{18}O}) record
           from a compilation of globally-distributed deep sea sediment cores
           \citep{Lisiecki.Raymo.2005}. Higher \chem{\delta^{18}O} values
           correspond to periods of lower temperatures \citep{Emiliani.1955}
           or lower global sea level, and thus higher ice volume stored in
           glaciers and ice sheets on land \citep{Shackleton.1967}.
           \textbf{(b)} Temperature anomalies ($\Delta T$) reconstructed from a
           central Antarctic ice core \citep[EPICA Dome~C,][]{Jouzel.etal.2007}.
           The grey bands indicate the approximate time span of the last
           glacial period of 110 to 10\,ka.}
  \label{fig:paleo-timeseries}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present \citep{Patterson.Kelso.2014}, and
           \textbf{(b)} during the last glacial maximum
           \citep{Ehlers.Gibbard.2007}.}
  \label{fig:paleo-glaciation}
\end{figure}

Nevertheless, the landform record is sparse in time and, most often, spatially
incomplete. Palaeo-ice sheets did not leave a continuous imprint on the
lanscape, and much of this evidence has been overprinted by subsequent glacier
re-advances and other geomorphological processes \citep{Kleman.1994,
Kleman.etal.2006, Kleman.etal.2010}.
Therefore, geomorphological reconstructions of former glacier extent require a
substantial amount of interpretation. This is where numerical ice sheet models,
incorporating the processes of glacier sliding \citep[e.g.,][]{Weertman.1957}
and deformation \citep[e.g.,][]{Nye.1953} observed on modern glaciers, can
help. Although these models alone contain too many uncertainties to reproduce
accurate ice sheet reconstructions during former glacial cycles
\citep[e.g.,][]{Hebeler.etal.2008}, they can be calibrated against geological
data where they exist \citep{Napieralski.etal.2007}, while allowing
physics-based, quantitative reconstructions of ice sheet sectors where they do
not \citep[e.g.,][]{Marshall.etal.2002, Tarasov.Peltier.2004}.

In addition, numerical ice sheet models provide quantitative insights on the
four-dimensional distribution of stresses and deformations in palaeo-ice sheets
and allow for reconstructions of their past thickness and volume evolution, which
are difficult to infer from geological evidence.
